### 2017-02-27 2017mergingmerges/section/04-Fusion.tex
blocks -> instructions

Fig.~\ref{fig:Fusion:Def:Top} defines the top-level function that fuses a pair of processes.
Function \ti{fusePair} fuses a pair of processes together, constructing a new process that computes the outputs of both.
The blocks are constructed by computing a fixpoint, starting at the initial labels of each process with empty input states.
Each block is computed with \ti{tryStepPair}, which statically chooses one of the two processes to execute, and any reachable blocks are added recursively until fixpoint is reached.
This implementation assumes the heap variables are distinct, which can easily be ensured by renaming.

@@

Fig.~\ref{fig:Fusion:Utils} contains definitions of some utility functions which are not specific to fusion.
Function \ti{channels} computes the $\ChanType_2$ map for a pair of processes.
Function \ti{outlabels} gets the set of output labels for an instruction - this is used when computing the fixpoint of the blocks map.
Function \ti{swaplabels} flips the order of the compound labels in an instruction.

>>>>

Fig.~\ref{fig:Fusion:Def:Top} defines the top-level function that fuses a pair of processes.
Function \ti{fusePair} fuses a pair of processes together, constructing a new process that computes the outputs of both.
The instructions are constructed by computing a fixpoint, starting at the initial labels of each process with empty input states.
Each instruction is computed with \ti{tryStepPair}, which statically chooses one of the two processes to execute, and any reachable instructions are added recursively until fixpoint is reached.
This implementation assumes the heap variables are distinct, which can easily be ensured by renaming.

@@

Fig.~\ref{fig:Fusion:Utils} contains definitions of some utility functions which are not specific to fusion.
Function \ti{channels} computes the $\ChanType_2$ map for a pair of processes.
Function \ti{outlabels} gets the set of output labels for an instruction - this is used when computing the fixpoint of the instructions map.
Function \ti{swaplabels} flips the order of the compound labels in an instruction.
